---
title: "Week 3 Homework"
author: "Edward Blaha"
format: 
  html: default
  docx: default
editor: source
---

## **Part 1 - Lines**

```{r}
graphics.off()

plot(x=0, type='n', xlim=c(-20,20), ylim=c(-20,20),
     xlab="X", ylab="Y", main=" Drawing y=4x+3 ")
abline(h=0, v=0, col = "gray")


abline(a=3, 
       b=4, 
       col = "seagreen2", 
       lty = "dashed")
text(4,6, "y=4x+3", col = "seagreen2")



```

**Bonus**

```{r}
graphics.off()

plot(x=0, type='n', xlim=c(-20,20), ylim=c(-20,20),
     xlab="X", ylab="Y", main=" Lines ")
abline(h=0, v=0, col = "gray")


abline(a=3, 
       b=4, 
       col = "seagreen2", 
       lty = "dashed")
text(4,6, "y=4x+3", col = "seagreen2")

abline(a=2,  b=6,  col = "turquoise4",  lty = "dotdash", lwd = 1)
abline(a=0.1,  b=2,  col = "violetred2",  lty = "solid", lwd = 2.5)
abline(a=1,  b=0.5,  col = "yellow",  lty = "longdash", lwd = 5)
abline(a=0,  b=4,  col = "red",  lty = "longdash", lwd = 1.5)
abline(a=2,  b=-6,  col = "turquoise4",  lty = "dotdash")
abline(a=0.1,  b=-2,  col = "black",  lty = "solid", lwd = 2.5)
abline(a=1,  b=-0.5,  col = "purple",  lty = "longdash")
abline(a=20,  b=100,  col = "orange",  lty = "longdash", lwd = 4)

```

## **Part 2: Protected Lands**
Find the mean, standard deviation, and range of each of the three variables: protected lands, GDP per capita, and total GDP.
Create a scatterplot where “protected lands” is on the Y axis and GDP per capita is on the X axis. Place a title on the graph and labels on the X and Y axis appropriately.
Create a scatterplot where “protected lands” is on the Y axis and total GDP is on the X axis. Place a title on the graph and labels on the X and Y axis appropriately.
Regress “protected lands” on GDP per capita.
Create a scatterplot where “protected lands” is on the Y axis and GDP per capita is on the X axis. Then, overlay the plot with a best fit line.
Regress “protected land” on total GDP.
Create a scatterplot where “protected lands” is on the Y axis and total GDP is on the X axis. Then, overlay the plot with a best fit line.
``` {R}
ProtectedLands <- read.csv("~/DataWrangling/Week4HW/DataWranglingWeek4/protected_lands.csv")
mean(ProtectedLands$protected_lands)
mean(ProtectedLands$gdp_percap)
mean(ProtectedLands$tot_gdp_bilions)

sd(ProtectedLands$protected_lands)
sd(ProtectedLands$gdp_percap)
sd(ProtectedLands$tot_gdp_bilions)

range(ProtectedLands$protected_lands)
range(ProtectedLands$gdp_percap)
range(ProtectedLands$tot_gdp_bilions)
```
